Multilevel regression models

### 2023-10-20 procesamiento/prod_analysis-full-sample.Rmd
Update prod_analysis-full-sample.Rmd

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
```

@@

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
  list(
    homclass = "Class-based network homogeneity",
    logrgdpna = "log GDP",
    palmaratio = "Palma Ratio",
    "homclass:palmawd" = "Homogeneity x Palma Ratio",
    top10 = "Share National Income - top 10%",
    "homclass:top10"= "Homogeneity x top 10",
    middle50 = "Share National Income -  bottom 50%",
    "homclass:middle50" = "Homogeneity x bottom 50",
    d10d1 = "Ratio D10/D01",
    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
    giniindex = "Gini (World Bank)",
    "homclass:giniindex" = "Homogeneity x Gini (WB)",
    ttheilge1 = "Theil Index",
    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
  )
texreg::knitreg(models_m,scalebox = 0.75,
                float.pos="h!",                
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
```

@@

save( list(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil),
     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
```

>>>>

save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-logit-homclass-full-macro.RData"))
```

@@

save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-logit-homclass-strong-macro.RData"))
```

@@

save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-logit-homclass-weak-macro.RData"))
```

@@

cap1=c("Cross-level interaction for Network homogeneity and Economic Inequality")
customcoef <- 
  list(
    homclass = "Class-based network homogeneity",
    logrgdpna = "log GDP",
    palmaratio = "Palma Ratio",
    "homclass:palmawd" = "Homogeneity x Palma Ratio",
    top10 = "Share National Income - top 10%",
    "homclass:top10"= "Homogeneity x top 10",
    middle50 = "Share National Income -  bottom 50%",
    "homclass:middle50" = "Homogeneity x bottom 50",
    d10d1 = "Ratio D10/D01",
    "homclass:d10d1" = "Homogeneity x Ratio D10/D01",
    giniindex = "Gini (World Bank)",
    "homclass:giniindex" = "Homogeneity x Gini (WB)",
    ttheilge1 = "Theil Index",
    "homclass:ttheilge1" = "Homogeneity x Theil Index"    
  )
texreg::knitreg(models_m,scalebox = 0.75,
                float.pos="h!",                
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-ologit-homclass-full-macro.RData"))
```

@@

save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-ologit-homclass-strong-macro.RData"))
```

@@

save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/fullsample-ologit-homclass-weak-macro.RData"))
```
